### 2016-05-13 2016-lrec-tyvmorph/poster.tex
a font adjustment that helps things fit
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68354 72bbbca6-d526-0410-a7d9-f06f51895060

\documentclass[fontscale=0.33,landscape,paperwidth=841mm,paperheight=1189mm]{baposter}  % fontscale=0.285, dvipdfm

@@

	}{ %Title (centered top)
		{%\vspace{0pt}\hspace{1cm} \
			{\titlefont \scshape{A finite-state morphological analyser for Tuvan}
			}
		}
	}{ %Authors (centered top, below title)
		\vspace{-0.6em}
		\begin{center}
			\begin{minipage}[t]{5.75em}
				\begin{spacing}{0.4}
				{Francis Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{9.25em}
				\begin{spacing}{0.4}
					{Jonathan Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{8em}
				\begin{spacing}{0.4}
					{Aziyana Bayyr-ool}\\
					{\footnotesize Сибирское отделение Российской академии наук\\\texttt{azikoa@mail.ru}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{6em}
				\begin{spacing}{0.4}
					{Aelita Salchak}\\
					{\footnotesize Тываның Күрүне Университеди\\\texttt{aelita\_74@mail.ru}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\includegraphics[height=6.2em]{img/Tuvsu}
		\includegraphics[height=6.2em]{img/soranif}
		%\hspace{2.5cm}
		\includegraphics[angle=90,height=6.7em]{apertium5b}%\hspace{-2em}
	}

>>>>

\documentclass[fontscale=0.35,landscape,paperwidth=841mm,paperheight=1189mm]{baposter}  % fontscale=0.285, dvipdfm

@@

	}{ %Title (centered top)
		{%\vspace{0pt}\hspace{1cm} \
			{\titlefont \scshape{A finite-state morphological analyser for Tuvan}
			}
		}
	}{ %Authors (centered top, below title)
		\vspace{-0.6em}
		\begin{center}
			\begin{minipage}[t]{7em}
				\begin{spacing}{0.4}
				{Francis M.\ Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{12em}
				\begin{spacing}{0.4}
					{Jonathan North Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{8em}
				\begin{spacing}{0.4}
					{Aziyana Bayyr-ool}\\
					{\footnotesize Сибирское отделение Российской академии наук\\\texttt{azikoa@mail.ru}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{6em}
				\begin{spacing}{0.4}
					{Aelita Salchak}\\
					{\footnotesize Тываның Күрүне Университеди\\\texttt{aelita\_74@mail.ru}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\includegraphics[height=6.2em]{img/Tuvsu}
		\includegraphics[height=6.2em]{img/soranif}
		%\hspace{2.5cm}
		\includegraphics[angle=90,height=6.7em]{apertium5b}%\hspace{-2em}
	}
